---
title: "Jose Trejo"
author: "Dr. J"
date: "6 Feb 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
print(xx)
#Drive_ltr <- strtrim(xx,2)
#yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
yy = 'My_photo.jpg'
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="I'm Confused")  
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg after first renaming the current one to Koala.jpg . 

## Where are you now?  
What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  How on a scale of 1 to 10 (1=low, 10=high) How you feel about periodic seat re-assignment, say how and why. Teams, have you ever worked on one in a class setting?  

I'm at the back of the class.  Computer 71791. On a scale of 1-10 I'm a 1. I don't like seat reassignment.  I worked on a team in an earlier class

###my answer     
  
   
     


## Others and You?   
What name do you prefer to be called by your classmates and instructor, if your buddys call you something but you want me to call you something else - what would that be? 

I prefer to be called Jose.
###my answer     
  
   
 




## Aspirations?   
What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?

In life I want to become a police officer I still don't know what school I want to transfer to. I want to get my bachelors in criminal justice. 
###my answer     
  
   
 




## Past adventures?  
Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?

Ive only ever gone to Mexico when I was little. Yes I been in the military I am in the Air Force Reserve. 
###my answer     
  
   
  




## Why are you taking Math 115?  
What grade do you need to attain in stats to not upset your future plans, What is your plan?
 
 I would just like to pass this class but im mainly going for an A. I dont fully know my plans yet.

###my answer     
  
   
 



## Homework Help and Getting Around?
On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?  Do you have a computer you can use at home? If so, what kind is it (windows, Apple, Linux)? Do you have internet access at home?  
How do you get to class? Are there issues that limit when you can be at the college?Where and when did you attend high school?  Do you currently have a job?

  
  
   
  







On a scale of 1-10 I would say im about a 6 or 7 because I grew up on computers so I'd say i know a thing or two. Yes I have internet acess at home I use a macbook. I atttended high school out here in Littlerock High School. 
### my answer   
  